### 2019-11-04 learning Logic/draft.tex
.
Case study updated

\subsection{Problem Setup}

@@

\subsection{Solution/Contribution draft}

@@

\begin{figure}[h]
	\includegraphics[scale=0.4]{auto}\caption{Models for the second automata example}
\end{figure}

@@

>>>>

\section{Problem Setup}

@@

\section{Solution/Contribution draft}

@@

\begin{figure}[h]
	\includegraphics[scale=0.4]{Fig/auto}\caption{Models for the second automata example}
\end{figure}

@@

\subsection{A mini case study}

Let us consider an office space with several rooms as illustrated in Fig. \ref{fig:office}. There are different objects in the office rooms. For simplicity, let us assume that each of the objects is either a desk (illustrated as a rectangle), or a chair (illustrated as a square), or a waste bin (illustrated as a circle). Consider a fully actuated robot with the initial position $x_0 \in \mathbb{R}^2$. We assume that the robot can recognize if it is close to a certain type of object or landmark in the environment; by close, we mean that the robot's state intersect with the object's/landmark's $\epsilon$-inflation (illustrated as dashed and dotted lines).

The set of atomic propositions is as follows:
\begin{itemize}
\item $\mathit{Room}_1,\ldots,\mathit{Room}_6, \mathit{Hall}$, stand for being in a particular room or in a hallway
\item $\mathit{Desk}$ stands for being close to a desk
\item $\mathit{Chair}$ stands for being close to a chair
\item $\mathit{Bin}$ stands for being close to a bin
\item $\mathit{Corner}$ stands for being close to a corner
\item $\mathit{Wall}$ stands for being close to a wall
\end{itemize}

The specification for the robot's behavior is given by the LTL formula:
$$G F (\mathit{Room}_1 \wedge \mathit{Bin}) \wedge \ldots \wedge G F (\mathit{Room}_6 \wedge \mathit{Bin}).$$

\begin{figure}
\centering
\includegraphics[width=\linewidth]{Fig/small-office} \caption{A mini case study office environment illustration.}
\label{fig:office}
\end{figure}
